---
title: "Movie reviewer"
author: "Bernart Mateusz 156072, Janiak Patryk 156053"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: "./03_logotyp_pp_wersja_ang/PP_logotyp_ANG_WHITE.png"
runtime: shiny
---
<style>
.navbar-header {
    display: flex;
    align-items: center;
    flex-direction: column;
    margin-top: 10px;
}
.navbar-brand {
    display: flex;
    justify-content: space-between;
    width: calc(100vw - 20px);    
}
.shiny-html-output.shiny-bound-output {
  position: absolute;
  width: calc(100% - 10px);
  height: calc(100vh - 278px)!important;
  top: 278px; 
}
</style>
<!-- 268px offset + 10px padding -->


```{r global, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(dplyr)
library(gridExtra)
library(cowplot)
library(stringr)
library(tidyr)
library(grid)
library(flexdashboard)
library(ggplot2)
library(plotly)
library(ggsci)
library(shiny)
library(lorem)
library(ggsci)

movies <- read.csv2("./imdb-movies-dataset.csv", sep = ",", dec = ".")
movies <- movies[1:1000, ]
flat_movies <- movies %>%
    separate_rows(Genre, sep = ",")
```

Datatable
=====================================

Column {data-width=650}
-----------------------------------------------------------------------

### Datatable

```{r}
library(DT)
prettyTable <- function(table_df, round_columns_func=is.numeric, round_digits=2) {
    DT::datatable(table_df, style="bootstrap", escape = FALSE, filter = "top", rownames = FALSE, extensions = "Buttons", options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) %>%
    formatRound(unlist(lapply(table_df, round_columns_func)), round_digits)
}
prettyTable(movies %>% select(-c(Review, Review.Title)) %>% mutate(Poster = paste('<img src="', Poster, '" style="width: 100%;" />')))
```

Page 2
=====================================

Column {.sidebar}
-----------------------------------------------------------------------

<div style="height: 500px"></div>

```{r}
sliderInput('years', label = 'Range of Years', step=1, min=min(flat_movies$Year), max = max(flat_movies$Year), value = c(min(flat_movies$Year),max(flat_movies$Year)))
```

Column
-----------------------------------------------------------------------

### Rating for selected years

```{r}
renderPlot({
  years = reactive(input$years)
  
  filtered = flat_movies %>% filter(years()[1] < Year & Year < years()[2])
  
  ggplot(
    filtered,
    aes(x = Year, y = Rating, color = Genre)
) +
    geom_point(alpha = 0.5) +
    xlim(min(flat_movies$Year), max(flat_movies$Year)) + 
    scale_color_jco() +
    theme_bw() +
    theme(legend.title = element_blank())
  }, res = 96)
```

Page 3
=====================================

Column {.sidebar}
-----------------------------------------------------------------------

<div style="height: 500px"></div>

```{r}
genres = flat_movies$Genre %>% unique()
selectInput("genres", label = "Selected genres", choices = genres, selected = genres %>% sample(5), multiple = TRUE)
```

Column
-----------------------------------------------------------------------

### Rating for selected genres

```{r}
renderPlot({
  genres = reactive(input$genres)
  
  filtered = flat_movies %>% filter(Genre %in% genres())
  
  ggplot(
    filtered,
    aes(x = Year, y = Rating, color = Genre)
) +
    geom_point(alpha = 0.5) +
    xlim(min(flat_movies$Year), max(flat_movies$Year)) + 
    scale_color_jco() +
    theme_bw() +
    theme(legend.title = element_blank())
  }, res = 96)
```

Directors
=====================================

Column {.sidebar}
-----------------------------------------------------------------------

<div style="height: 500px"></div>

```{r}
directors = flat_movies$Director %>% unique()
selectInput("single_director_page4", label = "Select a Director", choices = directors, selected = directors[1])
```
Column {data-width=300}
-----------------------------------------------------------------------

### Director gernes

```{r}
output$plot_directors <- renderPlotly({
  director <- reactive(input$single_director_page4)
  
  print(input$single_director_page4)
  print(typeof(director))
  print(typeof(flat_movies$Director))
  filtered <- flat_movies %>% filter(Director == director())
  print(director())
  
  genre_counts <- table(filtered$Genre)
  
  # Sort the genres based on their counts
  sorted_genres <- sort(genre_counts, decreasing = TRUE)
  
  # Get the top 5 genres
  top_genres <- names(sorted_genres)[1:5]
  
  # Combine the rest into "Other" category
  other_count <- sum(sorted_genres[-(1:5)])

  # Create a data frame for the pie chart
  pie_df <- data.frame(
    Genre = c(top_genres, "Other"),
    Count = c(sorted_genres[1:5], other_count)
  )
  pie_df <- na.omit(pie_df) %>% filter(Count != 0)
  print(pie_df)

  # Create the pie chart using ggplot
  pie_chart <- ggplot(pie_df, aes(x = Genre, y = Count, fill = Genre, text = paste(Genre, ": ", Count))) +
    geom_bar(stat = "identity") +
    # coord_polar(theta = "y") +
    theme_minimal() +
    labs(title = paste("Genres Distribution for", director()),
         x = "Gerne",
         y = "Count") +
    theme(legend.position="none")


  # Convert ggplot to plotly and specify tooltip
  ggplotly(pie_chart, tooltip = "text")
})
# Output the plotly chart
plotlyOutput("plot_directors")

```

Column {data-width=300}
-----------------------------------------------------------------------

### Director ratings

```{r}
output$plot_director_ratings <- renderPlotly({
  director <- reactive(input$single_director_page4)
  
  filtered <- flat_movies %>% 
    filter(Director == director() & !is.na(Rating)) %>%
    mutate(Ratings = round(Rating, 0)) %>%
    filter(!is.na(Ratings) & !is.na(Ratings))
  
  genre_counts <- as.data.frame(table(filtered$Ratings))

  # Create a data frame for the pie chart
  pie_df <- data.frame(
    Rating = genre_counts$Var1,
    Count = genre_counts$Freq
  )
  
  # Remove rows with 0 count and NA values
  pie_df <- pie_df %>% filter(Count != 0)
  
  print(pie_df)
  
  custom_palette <- c("#1f78b4", "#33a02c", "#e31a1c", "#ff7f00", "#6a3d9a", "#a6cee3")
  
  pie_chart <- ggplot(pie_df, aes(x = Rating, y = Count, fill = Rating, text = paste(Rating, ": ", Count))) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = custom_palette) + 
    theme_minimal() +
    labs(title = paste("Ratings Distribution for", director())) +
    theme(legend.position = "none")

  ggplotly(pie_chart, tooltip = "text")
})

plotlyOutput("plot_director_ratings")

```


About
=====================================

Column {data-width=650}
-----------------------------------------------------------------------
### About dataset

[IMDB Movies Dataset](https://www.kaggle.com/datasets/amanbarthwal/imdb-movies-data)

The IMDb Movies Dataset is one of the most extensive collections of movie-related data available. It includes a wide range of attributes such as titles, genres, cast and crew, release dates, ratings, and reviews. 

- Poster: link of the movie poster.
- Title: name of the movie.
- Year: year the movie was released.
- Certificate: age rating given to the movie (e.g., PG, R).
- Duration (min): length of the movie in minutes.
- Genre: genre(s) of the movie (e.g., Action, Comedy, Drama).
- Rating: IMDB user rating for the movie.
- Metascore: score from critics.
- Director: director(s) of the movie.
- Cast: main actors in the movie.
- Votes: number of votes the movie received on IMDB.
- Description: brief summary of the movie's plot.
- Review Count: total count of reviews.
- Review Title: title of the review.
- Review: movie review (review with highest votes on it).

This richness allows for in-depth analysis and insights into the film industry and audience preferences. It may be used in various scenarios - for example in recommendation system.

Column {data-width=350}
-----------------------------------------------------------------------

### About authors

- Bernart Mateusz 156072
- Janiak Patryk 156053

### Motivation

We want to get a nice grade 😊
